G85R vs WT (M + F)

### 2024-11-06 Arc1MeetingFigures.Rmd
pca

  FC.data = TKT.EdgeR.FC[, c("GRxWT.FC", "GRxWT.MC")]
  FDR.data = TKT.EdgeR[, c("GRxWT.FC", "GRxWT.MC")]
  mean.data = G85R.meancpm[, c('GRFC', 'WTFC', 'GRMC', 'WTMC')]

@@

@@

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
                  condition = A4V.groups$Group, 
                  group = paste0(groups$Genotype, groups$Sex),
                  TKT = groups$TKT)

@@

axis(1, at= 1:82, lwd.ticks = .5, labels = NA)
axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
     lwd.ticks = 1, cex.axis = 1,
     col.axis = 'lightgrey')
axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
     lwd.ticks = 1, cex.axis = 1,
     col.axis = 'black')

@@

legend('topright',
       legend = c('Female Silent', 'Female A4V',
                  'Male Silent', 'Male A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

#abline(v = 3, lty = 2, lwd = 2, col = 'black')
#abline(v = 9, lty = 2, lwd = 2, col = 'black')
#abline(v = 40, lty = 2, lwd = 2, col = 'black')

#points(x = c(3,9,40),
#       y = c(-11.75,-11.75,-11.75),
#       pch = 21,
#       cex = 4,
#       bg = hex('gold', .25),
#       col = 'grey25',
#       xpd = T)

#axis(1, at= c(3, 9, 40), lwd.ticks = 2, labels = c(3,9,40))

>>>>

  FC.data = TKT.EdgeR.FC[, c("GRxWT.FC", "GRxWT.MC")]
  FDR.data = TKT.EdgeR[, c("GRxWT.FC", "GRxWT.MC")]
  mean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'GR.M', 'WT.M')]

@@

  ##data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  ##data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[go.genes,c(1,3)], 1, mean),
                    WT = apply(mean.data[go.genes,c(2,4)], 1, mean))
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

@@

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
                  condition = A4V.meta$Group, 
                  group = paste0(groups$Genotype, groups$Sex),
                  TKT = groups$TKT)

@@

axis(1, at= 1:82, lwd.ticks = .5, labels = NA)
axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
     lwd.ticks = 1, cex.axis = 1,
     col.axis = 'lightgrey')
#axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
#     lwd.ticks = 1, cex.axis = 1,
#     col.axis = 'black')

@@

legend('topright',
       legend = c('Female Silent', 'Female A4V',
                  'Male Silent', 'Male A4V'),
       pch = c(21,23,21,23),
       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), 
                 hex(pcol[3], .5), hex(pcol[4], .5)),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

abline(v = 3, lty = 2, lwd = 2, col = 'black')
abline(v = 9, lty = 2, lwd = 2, col = 'black')
abline(v = 40, lty = 2, lwd = 2, col = 'black')

points(x = c(3,9,40),
       y = c(-11.75,-11.75,-11.75),
       pch = 21,
       cex = 4,
       bg = hex('gold', .25),
       col = 'grey25',
       xpd = T)

axis(1, at= c(3, 9, 40), lwd.ticks = 2, labels = c(3,9,40))

### 2024-11-06 GeneExpressionBoxPlots.Rmd
pca

```{r echo = F}
FBgn = 'FBgn0011817'
name = 'FBgn0011817: nmo'

@@

>>>>

FBgn = 'FBgn0032513'
name = 'STARD7'
FBgn = 'FBgn0028932'
name = 'CG16890'

@@

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.metab = mean.data

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.metab[,condition1]/mean.metab[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.metab)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")[row.names(GRxWT.C),]
GRxWT.OE = compare.conditions("F", "A")[row.names(GRxWT.C),]

GR.CxDf = compare.conditions("D", "E")[row.names(GRxWT.C),]
WT.CxDf = compare.conditions("B", "C")[row.names(GRxWT.C),]

GR.CxOE = compare.conditions("F", "E")[row.names(GRxWT.C),]
WT.CxOE = compare.conditions("A", "C")[row.names(GRxWT.C),]

GR.DfxWT.C = compare.conditions("D", "C")[row.names(GRxWT.C),]
GR.OExWT.C = compare.conditions("F", "C")[row.names(GRxWT.C),]

comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
                 GRF.CxOE = c("TktOEGR.F","GR.F"),
                 WTF.CxDf = c("TktDfWT.F","WT.F"),
                 WTF.CxOE = c("TktOEWT.F","WT.F"),
                 GRxWT.FC = c("GR.F","WT.F"), 
                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
                 GRM.CxOE = c("TktOEGR.M","GR.M"),
                 WTM.CxDf = c("TktDfWT.M","WT.M"),
                 WTM.CxOE = c("TktOEWT.M","WT.M"),
                 GRxWT.MC = c("GR.M","WT.M"), 
                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
                 GR.FxM = c("GR.F","GR.M"),
                 WT.FxM = c("WT.F","WT.M"))

metab.FC = data.frame('GRxWT.C' = GRxWT.C$FC,
                      'GRxWT.Df' = GRxWT.Df$FC,
                      'GRxWT.OE' = GRxWT.OE$FC,
                      'GR.CxDf' = GR.CxDf$FC,
                      'WT.CxDf' = WT.CxDf$FC,
                      'GR.CxOE' = GR.CxOE$FC,
                      'WT.CxOE' = WT.CxOE$FC,
                      'GR.DfxWT.C' = GR.DfxWT.C$FC,
                      'GR.OExWT.C' = GR.OExWT.C$FC)
row.names(metab.FC) = row.names(GRxWT.C)
metab.FC = log2(metab.FC)

metab.FDR = data.frame(GRxWT.C = GRxWT.C$p,
                       GRxWT.Df = GRxWT.Df$p,
                       GRxWT.OE = GRxWT.OE$p,
                       GR.CxDf = GR.CxDf$p,
                       WT.CxDf = WT.CxDf$p,
                       GR.CxOE = GR.CxOE$p,
                       WT.CxOE = WT.CxOE$p,
                       GR.DfxWT.C = GR.DfxWT.C$p,
                       GR.OExWT.C = GR.OExWT.C$p)
row.names(metab.FDR) = row.names(GRxWT.C)

colnames(mean.metab) = as.character(genotypes[colnames(mean.metab)])

colnames(norm.data) = as.character(genotypes[substr(colnames(norm.data),1,1)])

metab = 'D-sedoheptulose-7-phosphate'
name = 'D-sedoheptulose-7-phosphate'

metab = data.frame(data = as.numeric(norm.data[metab,]), 
                   group = colnames(norm.data), 
                   geno = colnames(norm.data))

metab$group = factor(metab$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                             "GR", "TktDfGR", "TktOEGR"))

metab$geno = factor(substr(metab$group, (nchar(as.character(metab$group)) -1), nchar(as.character(metab$group))), 
                     levels = c("WT", "GR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(metab$data), max(metab$data)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

boxplot(metab$data~metab$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightyellow", 3),
                rep("lightgreen", 3)))

points(x=as.numeric(factor(metab$group)),
       y=metab$data,
       cex=1.25,
       pch=21,
       bg=c('gold3',"darkgreen")[as.numeric(factor(metab$geno))])

axis(side = 1,
     at = c(2, 5, 8, 11),
     labels = c("Silent", "G85R","Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -.5,
     cex.axis = 2)

xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

### 2024-11-06 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
pca

sigsKEY = GeneIDKey[sigs,]
sigs = sigsKEY$Symbol
bgKEY = GeneIDKey[bg,]
bg = bgKEY$Symbol

@@

>>>>

sigs = row.names(A4V.FDR)[A4V.FDR[, "AvS40FT"] <= .05]
bg = row.names(A4V.FDR)[A4V.FDR[, "AvS40FT"] <= 1]

sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
bg = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]

sigsKEY = GeneIDKey[sigs,]
sigs = unique(na.omit(sigsKEY$Symbol))
bgKEY = GeneIDKey[bg,]
bg = unique(na.omit(bgKEY$Symbol))

@@

##GFsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
##GMsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
#AF3Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
#AF9Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
#AF40Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
#AM3Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
#AM9Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
